\textcolor{violet}{Reverse Correlation Uncovers More Complete Tinnitus Spectra \vspace{0.25cm}}

### 2023-03-27 paper/short/main_wc995.tex
Edits from lab meeting

% INTRO PARAGRAPH 3/3
Here, we validate RC as a method for characterizing a more complete psychoacoustic tinnitus spectrum (PTS) for tinnitus sounds.
To that end, normal-hearing participants completed an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound.
The estimated PTS was subsequently validated against the targets.
Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC.

@@

Ten ($n=10$) normal-hearing subjects listened to \textit{A-X} trials containing a target sound ($A$) followed by a stimulus ($X$).
$X$ was randomly generated for each trial, while $A$ remained the same within a block of $100$ trials (Fig.
\ref{fig:experimentdiagram}).
Subjects completed two (2) blocks per target sound ($p=200$ total trials per subject).
Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
Presentation level (in dB SPL) was not recorded.
Procedures were approved by the UMass IRB.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{gfx/reconstruction_spectra_cropped.pdf}
    \caption{Reconstructions of the PTS capture many salient features of tinnitus spectra.
    The black trace indicates the target,
    while colored traces plot exemplar human reconstructions.
    The top row shows standardized power levels within each frequency bin.
    The bottom row maps the $8$-dimensional bin domain
    to a $11025$-dimensional frequency domain with the unbinned power spectral density of the targets shown in gray.}
    \label{fig:spectra}
\end{figure}

>>>>

% INTRO PARAGRAPH 3/3
Here, we validate RC as a method for characterizing individuals' internal representations of tinnitus
more completely.
To that end, normal-hearing participants completed an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound,
yielding frequency spectrum estimates of their tinnitus representation.
The estimated spectra were subsequently validated against the target tinnitus sounds.
Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC.

@@

Ten ($n=10$) normal-hearing subjects listened to \textit{A-X} trials containing a target sound ($A$) followed by a stimulus ($X$).
$X$ was randomly generated for each trial, while $A$ remained the same within a block of $100$ trials (Fig.
\ref{fig:experimentdiagram}).
Subjects completed two (2) blocks per target sound ($p=200$ total trials per subject).
Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
Presentation level was not recorded.
Procedures were approved by the UMass IRB.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{gfx/reconstruction_spectra_cropped.pdf}
    \caption{Reconstructions of the tinnitus spectra capture many salient features of the target sounds.
    The black trace indicates the target,
    while colored traces plot exemplar human reconstructions.
    The top row shows standardized power levels within each frequency bin.
    The bottom row maps the $8$-dimensional bin domain
    to a $11025$-dimensional frequency domain with the unbinned power spectral density of the targets shown in gray.}
    \label{fig:spectra}
\end{figure}
